GFW Dataset - Fishing effort by year, EEZ/high seas region, and flag state (2016-2019)

### 2020-04-24 scripts/other-analyses/supplementary-gfw-datasets/gfw_dataset_for_pew.Rmd
and read me

# save
write_csv(flag_state, paste0(results_dir, "gfw_for_pew_totals_by_year_flag.csv"))
```

@@

# save
write_csv(area, paste0(results_dir, "gfw_for_pew_totals_by_year_flag_eez_territorial.csv"))
```

>>>>

# save
write_csv(flag, paste0(results_dir, "gfw_for_pew_totals_by_year_flag.csv"))
```

@@

# save
write_csv(terr, paste0(results_dir, "gfw_for_pew_totals_by_year_flag_eez_territorial.csv"))
```
